---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# tmod

<!-- badges: start -->
<!-- badges: end -->

Tmod is a suite of gene set enrichment algorithms, visualizations and
utilities which comes bundled with a few libraries of gene sets
("modules"). Following features distinguish tmod from other packages:

 * "panel plot" visualizations which allow to compare results of gene set
   enrichments;
 * several enrichment algorithms are implemented in tmod, in particular the
   very efficient, versatile and
   [reproducible](https://academic.oup.com/bioinformatics/article/35/24/5146/5511403)
   algorithm called "CERNO";
 * it includes a library of gene sets derived from clustering of gene
   expression data from human blood, which is especially useful in
   functional analysis in infection and immune responses.

## Installation

You can install the released version of tmod from [CRAN](https://CRAN.R-project.org/) with:

``` r
install.packages("tmod")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("january3/tmod")
```
## Tmod manual

 * Access the documentation using `vignette("tmod")`
 * Full user manual is found [here](https://january3.github.io/tmod/)

## Example usage


```{r include=FALSE}
library(ggplot2)
library(cowplot)
theme_set(theme_minimal())
```





```{r}
library(tmod)
data(EgambiaResults)
tt <- EgambiaResults

## gene set enrichment analysis
res <- tmodCERNOtest(tt$GENE_SYMBOL)
head(res)
```

A few visualizations:


```{r eval=FALSE}
## overview
ggPanelplot(res)

## evidence plots
ggEvidencePlot(tt$GENE_SYMBOL, "LI.M16")
ggEvidencePlot(tt$GENE_SYMBOL, "LI.M37.0", gene.labels = FALSE)
ggEvidencePlot(tt$GENE_SYMBOL, "DC.M3.4")
```


```{r fig.width=10,fig.height=10,echo=FALSE}
## overview
g1 <- ggPanelplot(res)

## evidence plots
g2 <- ggEvidencePlot(tt$GENE_SYMBOL, "LI.M16") + ggtitle("LI.M16")
g3 <- ggEvidencePlot(tt$GENE_SYMBOL, "LI.M37.0", gene.labels = FALSE) +
  ggtitle("LI.M37.0")

g4 <- ggEvidencePlot(tt$GENE_SYMBOL, "DC.M3.4") + ggtitle("DC.M3.4")
plot_grid(g1, g2, g3, g4)
```




